A fast unified model for parsing and sentence understanding

### 2016-03-15 writing/hard_stack_paper/paper.tex
More minor improvements re: comments

A shift-reduce parser accepts a sequence of input tokens $\mathbf x = (x_1, \dots, x_N)$ and transitions $\mathbf t = (t_1, \dots, t_T)$. It reads left-to-right over the input transition sequence, combining the input tokens $\mathbf x$ incrementally into a tree structure. For any binary-branching tree structure over $N$ words, this requires $T = 2N - 1$ transitions. \todo{[JG] Try to introduce transitions before referring to the transition var $\mathbf t$. Maybe say that each $t\in\{\shift, \reduce\}$ }

@@

We implemented the feedforward of the SPINN-NP-NT model (which is equivalent to a standard TreeRNN) in C++/CUDA in order to compare to the performance of a standard CPU-based TreeRNN solution \cite{irsoy2014deep}. Figure~\ref{fig:speed} compares the runtime performance of the two models computing representations on data from the Stanford Sentiment Treebank \todo{cite}. Each model is restricted to run on sentences of 30 tokens or fewer (for the SPINN model, this means we iterate over a sequence of 59 transitions. We fix the model dimensionality and word embedding dimensionality at 300 for all tests. \todo{[JG] Explain why we implemented *just* feedforward in this style. (Something like: Theano is convenient for training but very non-optimal for our model.)}

The CPU reference model is implemented in C++ and uses a single-core Eigen linear algebra backend. The implementation is a simplified version of the TreeRNN from \citealt{irsoy2014deep}\footnote{The original code for this model is available at \url{https://github.com/oir/deep-recursive}. We plan to release our modified code.}, modified to exactly match the computation performed by our GPU model. We run the CPU performance test on a 2.20-GHz Intel Xeon processor with hyperthreading enabled. Our GPU model is implemented in C++ and CUDA, and will be released with the rest of our code. We test its performance on an NVIDIA Titan X GPU.

>>>>

A shift-reduce parser accepts a sequence of input tokens $\mathbf x = (x_1, \dots, x_N)$ and transitions $\mathbf t = (t_1, \dots, t_T)$, where each $t_i \in \{\shift, \reduce\}$ specifies a \shift~or \reduce~transition (described below). It reads left-to-right over the input transition sequence, combining the input tokens $\mathbf x$ incrementally into a tree structure. For any binary-branching tree structure over $N$ words, this requires $T = 2N - 1$ transitions.

@@

We implemented the feedforward of the SPINN-NP-NT model (which is equivalent to a standard TreeRNN) in C++/CUDA in order to compare to the performance of a standard CPU-based TreeRNN solution from \citet{irsoy2014deep}. Such a standard TreeRNN implementation operates on a single example at a time and is thus not feasible to run on a GPU.\footnote{We chose to reimplement and evaluate only the thin-stack feedforward (not training/backpropagation) in C++/CUDA, as this is the more critical performance metric for real-world applications.}

Figure~\ref{fig:speed} compares the runtime performance of the two models computing representations on data from the Stanford Sentiment Treebank \todo{cite}. Each model is restricted to run on sentences of 30 tokens or fewer (for the SPINN model, this means we iterate over a sequence of 59 transitions). We fix the model dimensionality and word embedding dimensionality at 300 for all tests.

The CPU reference model is implemented in C++ and uses a single-core Eigen linear algebra backend. The implementation is a simplified version of the TreeRNN from \citet{irsoy2014deep}\footnote{The original code for this model is available at \url{https://github.com/oir/deep-recursive}. We plan to release our modified code.}, modified to exactly match the computation performed by our GPU model. We run the CPU performance test on a 2.20-GHz Intel Xeon processor with hyperthreading enabled. Our GPU model is implemented in C++ and CUDA, and will be released with the rest of our code. We test its performance on an NVIDIA Titan X GPU.
